Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-25 paper.qmd
Arrange scripts

```{r}
#| label: fit_model-two-curvy

@@

```{r}
#| label: rm-lwd-bin-error

@@

```{r}
#| label: combine-data-two_curvy

@@

<!--Projections-->
```{r}
#| label: five-gau-proj-tsne-model

@@

```{r}
#| label: five-gau-proj-umap-model

@@

```{r}
#| label: five-gau-proj-pacmap-model

@@

```{r}
#| label: error-model-one-dens-clust

@@

```{r}
#| label: combine-data-mnist

@@

<!-- Fit the model and compute error-->
```{r}
#| label: hexbin-mnist

@@

```{r}
#| label: img-diff-pos

>>>>

<!--two_nonlinear/06_gen_model_with_tSNE.R-->
```{r}
#| label: fit_model-two-curvy

@@

<!--two_nonlinear/05_gen_rm_lwd_mse.R-->
```{r}
#| label: rm-lwd-bin-error

@@

<!--two_nonlinear/04_gen_mse_for_diff_methods.R-->
```{r}
#| label: combine-data-two_curvy

@@

<!--Projections-->
<!--five_gau_clusters/02_gen_model_with_tSNE.R-->
```{r}
#| label: five-gau-proj-tsne-model

@@

<!--five_gau_clusters/03_gen_model_with_UMAP.R-->
```{r}
#| label: five-gau-proj-umap-model

@@

<!--five_gau_clusters/04_gen_model_with_PaCMAP.R-->
```{r}
#| label: five-gau-proj-pacmap-model

@@

<!--one_c_shaped_dens_structure/03_gen_model_with_tSNE.R-->
```{r}
#| label: error-model-one-dens-clust

@@

<!--mnist/04_gen_mse_for_diff_methods.R-->
```{r}
#| label: combine-data-mnist

@@

<!-- Fit the model and compute error-->
<!--mnist/05_gen_model_with_tSNE.R-->
```{r}
#| label: hexbin-mnist

@@

<!--mnist/03_gen_images.R-->
```{r}
#| label: img-diff-pos
